### 2015-10-29 postdoctoral/gamma_functions.tex
switch to using gamma over nu

  \begin{theorem}
    \(X=\varprojlim \{2, \nu, L\}\cong \check L\)
  \end{theorem}

@@

    We first observe that if \(\vect x(b)=1\), then for all \(a\leq b\),
    \(\vect x(a)\in\nu(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
    without loss of generality that \(\vect x(a)=0,\vect y(a)=1\), so
    \(\vect x<\vect y\). Also, whenever \(\vect x(b)=1\), we have that \(b<a\),
    so \(\vect y(b)=1\), preventing \(\vect y<\vect x\). Finally if
    \(\vect x<\vect y\) and \(\vect y<\vect z\), take \(a,b\) with
    \(\vect x(a)=0\), \(\vect y(a)=1\),\(\vect y(b)=0\),\(\vect z(b)=1\). It
    follows that \(a<b\) so \(\vect z(a)=1\) and \(\vect x<\vect z\).

@@

  \begin{corollary}
    \(
      \varprojlim \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \nu, \alpha\}
      \cong \check\alpha =
    \alpha+1\) for free.
  \end{proof}

@@

  \begin{theorem}
    \(Y=\varprojlim^\star \{2, \nu, L\}\cong \hat L\).
  \end{theorem}

  \begin{proof}
    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \nu, L\}\) with
    the linear order described above. We claim that if \(\phi\) is the
    characteristic function for a subset of \(L\), then \(\phi\)
    is an order isomorphsim between \(\<Y,\leq\>\) and
    \(\<\hat L,\subseteq\>\).

@@

  \begin{corollary}
    \(
      \varprojlim^\star \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every infinite limit or finite ordinal \(\alpha\).
  \end{corollary}

>>>>

  \begin{theorem}
    \(X=\varprojlim \{2, \gamma, L\}\cong \check L\)
  \end{theorem}

@@

    We first observe that if \(\vect x(b)=1\), then for all \(a\leq b\),
    \(\vect x(a)\in\gamma(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
    without loss of generality that \(\vect x(a)=0,\vect y(a)=1\), so
    \(\vect x<\vect y\). Also, whenever \(\vect x(b)=1\), we have that \(b<a\),
    so \(\vect y(b)=1\), preventing \(\vect y<\vect x\). Finally if
    \(\vect x<\vect y\) and \(\vect y<\vect z\), take \(a,b\) with
    \(\vect x(a)=0\), \(\vect y(a)=1\),\(\vect y(b)=0\),\(\vect z(b)=1\). It
    follows that \(a<b\) so \(\vect z(a)=1\) and \(\vect x<\vect z\).

@@

  \begin{corollary}
    \(
      \varprojlim \{2, \gamma, \alpha\}
      \cong
      \alpha+1
    \)
    for every ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \gamma, \alpha\}
      \cong \check\alpha =
    \alpha+1\) for free.
  \end{proof}

@@

  \begin{theorem}
    \(Y=\varprojlim^\star \{2, \gamma, L\}\cong \hat L\).
  \end{theorem}

  \begin{proof}
    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \gamma, L\}\) with
    the linear order described above. We claim that if \(\phi\) is the
    characteristic function for a subset of \(L\), then \(\phi\)
    is an order isomorphsim between \(\<Y,\leq\>\) and
    \(\<\hat L,\subseteq\>\).

@@

  \begin{corollary}
    \(
      \varprojlim^\star \{2, \gamma, \alpha\}
      \cong
      \alpha+1
    \)
    for every infinite limit or finite ordinal \(\alpha\).
  \end{corollary}
